Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-06-13 survey/survey.tex
fixed typo
.

>>>>

%%%
\subsection{Spacetime Model}

To gain an intuition for resources, we think of the types as possible
events, and of the values as consistent timelines of events. From this
perspective, $A * B$ denotes spatial composition, where both $A$ and
$B$ must happen in \emph{some} order, and $A + B$ denotes temporal
composition, where exactly one of $A$ and $B$ must happen at a given
time. The event $1$ is then trivial, and $0$ is impossible.  We
visualize the denotation of $1$ as a point in space, and $0$ as empty
space. The denotation of $A + B$ is the denotation of $A$ drawn on top
of the denotation of $B$ and separated by a border, and the denotation
of $A * B$ is just the denotation of $A$ written next to the
denotation of $B$. Now we can formally define a consistent timeline
recursively on the structure of a diagram:

\begin{itemize}
\item An endpoint (the denotation of $1$) has exactly one timeline
  through it.  Empty space (the denotation of $0$) has no timelines
  through it.
\item A timeline through a stack of alternatives
  $A_1 + A_2 + \cdots + A_n$ is a timeline through exactly one of the
  possible alternatives.
\item A timeline through a spatial composition of cells
  $A_1 * A_2 * \cdots * A_n$ is a timeline through \emph{all} of the
  cells, in some order.
\end{itemize}

For example, let $2$ be the type $1 + 1$. The following would be a
consistent timeline through the diagram for
$((2 + 2) * (2 + 2)) + ((2 + 2) * (2 + 2))$ times itself as shown in
the left two boxes. The right two boxes show the trade-off between
space and time encoded in distributivity. Since a timeline must pass
through a column in exactly one point, the two boxes on the right have
the same timelines:
\begin{center}
\includegraphics[scale=0.3]{images/tall-tl-1}
\quad
\includegraphics[scale=0.3]{images/tall-tl-2}
\qquad\qquad\qquad
\includegraphics[scale=0.3]{images/distrib-1}
\qquad
\includegraphics[scale=0.3]{images/distrib-2}
\end{center}
